No sign of recovery

### 2018-05-22 Manuscript.Rmd
Edits in Manuscript. Remove site with very high deposition rate.

```{r communitytrends, results='asis', }
res <- tibble(Measures = c("Alpha-diversity", "Beta-diversity", "Gamma-Diversity", "Temperature value", "Huminity value", "Nutrients value", "Light value"),
              'Period 1' = NA,
              'Period 2' = NA,
              'Period 3' = NA,
              'Temporal-Trend' = NA,
              '2.5%' = NA,
              '97.5%' = NA)

# Alpha diversity
res[1, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$SR, surv$Visit, mean)
tmp <- stan_glmer(SR ~ yr + (yr|aID_STAO), data = surv, family = poisson,
                  cores = ncores, iter = niter)
res[1, "Temporal-Trend"] <- fixef(tmp)["yr"]
res[1, c('2.5%', '97.5%')] <- posterior_interval(tmp, pars = "yr")

@@

# Gamma diversity
res[3, c("Period 1", "Period 2", "Period 3")] <- tapply(pl$aID_SP, pl$Visit, function(x) length(unique(x)))

# Mean community index
res[4, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$T, surv$Visit, mean), 2)
tmp <- summary(lme(T ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[4, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[4, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

res[5, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$F, surv$Visit, mean), 2)
tmp <- summary(lme(F ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[5, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[5, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

res[6, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$N, surv$Visit, mean), 2)
tmp <- summary(lme(N ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[6, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[6, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

res[7, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$L, surv$Visit, mean), 2)
tmp <- summary(lme(L ~ yr, random = ~ yr|aID_STAO, data = surv))$tTable
res[7, "Temporal-Trend"] <- formatC(tmp["yr", "Value"], format = "f", digits = 3)
res[7, "P-value"] <- formatC(tmp["yr", "p-value"], format = "f", digits = 3)

print(xtable(res, align = c("l", "l", rep("r", 6)), digits = ndigits, label = "temporaltrends", caption = "Average measures of community structure for the three survey periods (in each period all sites are surveyed once). The temporal trends and p-values are based on linear mixed models with normal distribution (except for alpha-diversity with Poisson distribution) with site-ID as random effect. Temporal-trends are given per 10 years. Linear mixed models could not be applied for beta- and gamma-diversity because measures are not available for the single sites."), include.rownames=FALSE)
```

The different measures of total community structure suggested that plant communities in mountain hay meadows were stable between 2003 and 2017 (Table \@ref(communitytrends)): for each of the three 5-year survey periods the averages of alpha-, beta- and gamma-diversity and the average Ellenberg values for temperature, nutrients, light and huminity did not vary much among the three sampling periods. For all measures, all p-values of the average temperal trends per site were $>0.05$ and only in the case of the average temperature value of the species the p-value was $<0.1$. Note that beta- and gamma-diversity are note available for single sites and thus mixed models to calculate the p-value could not be applied.

```{r turnover}
tt <- rbind(
  sites %>% transmute(
    change = change1, 
    nochange = nochange1,
    period = 1),
  sites %>% transmute(
    change = change2, 
    nochange = nochange2,
    period = 2))
mod <- glm(cbind(change, nochange) ~ period, data = tt, family = binomial)
```

The temporal stability as inferred from the community measures were, however, in contrast to the large  observed temporal turnover of recorded species. The average percentage $\pm$ SD of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seems that the turnover from the first/second survey to the temporal turnover of the second/third survey slightly decreased (95% Credible interval of the change in turnover estimated from a Binomial generalized linear model: `r coef(mod)[2]`; p = `r summary(mod)$coefficients["period", "Pr(>|z|)"]`).

```{r diffromrandom}
# Function to sample community and callculate CM
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

# Prepare data from one site and calculate mean and CrI for sample and mean for real community
getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    summarise(Occ1 = sum(Visit == 1),
              Occ2 = sum(Visit == 2),
              Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

@@

# Make calculations and plot
tres <- makesim("N", gain = FALSE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNloss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses")

@@

multiplot(pNloss, pNgain, cols = 2)

@@

t.test(sites$ngain)
t.test(sites$nlost)

lm(ngain ~ Inclination + Temperature + Precipitation  + NTOT, data = sites) %>% 
  tidy

plot(sites$ngain, sites$nlost)

tapply()

@@

>>>>

```{r communitytrends, results='asis', }
res <- tibble(Measures = c("Alpha-diversity", "Beta-diversity", "Temperature value", "Huminity value", "Nutrients value", "Light value"),
              'Period 1' = NA,
              'Period 2' = NA,
              'Period 3' = NA,
              'Trend' = NA,
              '5%' = NA,
              '95%' = NA,
              'Trend > 0' = NA)

# Alpha diversity
res[1, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$SR, surv$Visit, mean)
load("Modelfit/SR-trend.RData")
res[1, "Trend"] <- fixef(mod)["yr"]
res[1, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[1, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

@@

# Mean community index
res[3, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$T, surv$Visit, mean)
load("Modelfit/T-trend.RData")
res[3, "Trend"] <- fixef(mod)["yr"]
res[3, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[3, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[4, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$F, surv$Visit, mean), 2)
load("Modelfit/F-trend.RData")
res[4, "Trend"] <- fixef(mod)["yr"]
res[4, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[4, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[5, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$N, surv$Visit, mean), 2)
load("Modelfit/N-trend.RData")
res[5, "Trend"] <- fixef(mod)["yr"]
res[5, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[5, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[6, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$L, surv$Visit, mean), 2)
load("Modelfit/L-trend.RData")
res[6, "Trend"] <- fixef(mod)["yr"]
res[6, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[6, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

print(xtable(res, align = c("l", "l", rep("r", 7)), digits = ndigits, caption = "Average measures of community structure for the three sampling periods (period 1: 2003-2007; period 2: 2008-2012; period: 2013-2017). The temporal trends are given as  change per 10 years and were estimated from linear mixed models with normal distribution (except for alpha-diversity with Poisson distribution and a log-link function) with site-ID as random intercept and slope effect. The measure of precision for the temporal trend is given as the 5% and 95% quantiles of the marginal posterior distribution. Finally, the probability that the linear trend is <0 is given. Linear mixed models were not applicable for beta-diversity because measures for beta-diversity were not available for the single sites."), include.rownames=FALSE)
```

The different measures of total community structure suggested that plant communities in mountain hay meadows were stable between 2003 and 2017 (Table \@ref(communitytrends)): for each of the three 5-year survey periods the averages of alpha- and beta-diversity and the average Ellenberg values for temperature, nutrients, light and huminity did not vary much among the three sampling periods. Except for average Ellenberg value for temperature, the 90% credible-interval of the temporal trend contained zero and the probability of a trend $>0$ was rather close to 0.5.

```{r turnover}
load("Modelfit/turnover-trend.RData")
tmp <-  posterior_interval(mod, pars = "period")
CrI <- paste0(round(tmp[1,1], ndigits), " - ", round(tmp[1,2], ndigits))
```

The temporal stability as inferred from the community measures were, however, in contrast to the large  observed temporal turnover of recorded species. The average percentage $\pm$ SD of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seems that the turnover from the first/second survey to the temporal turnover of the second/third survey moderately decreased (90% Credible interval of the change in turnover estimated from a Binomial generalized linear model: `r CrI`).

```{r diffromrandom}
# Number of simulations
nsim <- 100

# Function to sample community and callculate CM
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

# Prepare data from one site and calculate mean and CrI for sample and mean for real community
getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    dplyr::summarise(Occ1 = sum(Visit == 1),
                     Occ2 = sum(Visit == 2),
                     Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

@@

# Make calculations and plot for T value
tres <- makesim(EL = "T", gain = FALSE)

tres <- makesim("N", gain = TRUE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains") 
# Make calculations and plot for N value
tres <- makesim(EL = "N", gain = FALSE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNloss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses")

@@

@@

@@

```{r, fig.cap="Noch einfügen."}
multiplot(pNloss, pNgain, cols = 2)
```
